A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-02-22 doc/large_strain.tex
Change colour of J-P's suggestions
Add a reference to one of the largest deal.II runs

\newcommand{\changeJP}[1]{\textcolor{blue}{#1}}
\newcommand{\todojp}[1]{\todo[inline,color=red!40,size=\small]{TODO (J-P): #1}}

@@

\changeJP{Extension of this study from the node level to the cluster level is beyond the scope of this work.
However, as a step in this direction we have performed a preliminary study of the weak scalability of the implementation.
Table \ref{tab:weak_3d} demonstrates a good weak scaling up to 1280 processes\footnote{%
This corresponds to 64 nodes, which is the maximum we could request on the RRZE Emmy HPC cluster.
} of the wall time per matrix-vector product and per iteration in the CG solver for the 3D problem with a tri-quadratic basis.
This confirms that the matrix-free and multigrid frameworks implemented in the \texttt{deal.II} library can provide a competitive solution for cluster-sized problems as well.
}

>>>>

\newcommand{\changeJP}[1]{\textcolor{red}{#1}}
\newcommand{\todojp}[1]{\todo[inline,color=red!40,size=\small]{TODO (J-P): #1}}

@@

\changeJP{Extension of this study from the node level to the cluster level is beyond the scope of this work.
However, as a step in this direction we have performed a preliminary study of the weak scalability of the implementation.
Table \ref{tab:weak_3d} demonstrates a good weak scaling up to 1280 processes\footnote{%
This corresponds to 64 nodes, which is the maximum we could request on the RRZE Emmy HPC cluster.
} of the wall time per matrix-vector product and per iteration in the CG solver for the 3D problem with a tri-quadratic basis.
This confirms that the matrix-free and multigrid frameworks implemented in the \texttt{deal.II} library can provide a competitive solution for cluster-sized problems as well,
also compare \cite[Figure 7]{Krank2017} for scaling results for up to 147'456 CPU cores and 34.4 billion degrees of freedom for an incompressible flow problem.
}
